Tabular Constraint Learning

### 2016-04-11 Paper/ECAI/tabular.tex
Tias suggestion
removed algo, added an explation in text :

\textbf{Motivation}:
\begin{itemize}
  \item File generated from model, model got lost, need to reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

@@

\section{Approach to Tabular Constraint Learning}
Here we describe how the problem of Condensed Tabular Constraint Learning can be solved. The algorithm mimics the structure of the problem in the following way: first we need to order constraints in the order of specificity, then for each constraint we need to find possible candidate groups,\sergey{continue here..}

@@

\samuel{Running example (RANK?)}
\paragraph{Constraint ordering} $\constrainttorder(\constraints,\dependencies)$ uses the DAG \dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of \dependencies. Also, if there is a construction edge from $C_1$ to $C_2$, and $X$ is not a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$. If there is a sumsumption edge from $C_1$ to $C_2$ and $X$ is a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$.

@@

\samuel{Move to beginning without algo}
\subsection{Workflow}
\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $D$ -- dataset, \constraints -- constraints, \dependencies -- dependencies \\(optional: tables $T$, groups $G$)
    \State \textbf{Output:} $S$ -- learned constraints with their satisfaction assignment
    \If{$T$ is \textbf{not} provided}
      \State $T \gets \extracttables(D)$
    \EndIf
    \If{$G$ is \textbf{not} provided}
      \State $G \gets \extractgroups(D, T)$
    \EndIf
    \State $S \gets \learnconstraints(G,\constraints,\dependencies)$
    \State \Return $S$
\end{algorithmic}
\caption{Workflow}
\label{algo:workflow}
\end{algorithm}

\textbf{Approach}
\begin{itemize}
  \item Notation
  \item Algorithm (select constraints, find assignments, find solutions)
\end{itemize}

\samuel{Move next to subgroup satisfaction search}
\section{Declarative modeling}
\sergey{We need to fit ASP, Minizinc and all that here, I mean it is supposed to be an important point after all}

>>>>

\textbf{Motivation}:
\samuel{Suggest better table layouts / formula translation}
\begin{itemize}
  \item File generated from model, model got lost, need to reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

@@

\section{Approach to Tabular Constraint Learning}
As we have seen the statement before assumes the set of groups to be given. It is often, however, not the case and a possible approach is to extract the groups from the CSV file directly. In our system, we have implement the group construction step using the type-consistency check. \sergey{Samuel, we need details here, I think} In general, separating data from a header is a task on its own  \cite{header} and goes beyond the scope of this paper.

Another solution to the group extraction problem is to make it interactive, when a user can select the groups in the spreadsheet or correct automatically generated groups. We regard this approach to be a possible future direction in the system development. Later in the paper we assume the groups to be given.

Now we describe how the problem of Condensed Tabular Constraint Learning can be solved. The algorithm mimics the structure of the problem in the following way: first we need to order constraints in the order of specificity, then for each constraint we need to generate possible candidate groups, and in the next step we find the subgroups satisfying the constrain. After an iteration we accumulate all solutions and proceed to the next constraint.

@@

\samuel{Running example (RANK?)}
\paragraph{Constraint ordering} $\constrainttorder(\constraints,\dependencies)$ uses the DAG \dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of \dependencies. Also, if there is a solid edge from $C_1$ to $C_2$, and $X$ is not a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$. If there is a dashed edge from $C_1$ to $C_2$ and $X$ is a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$.

@@

\samuel{Move to beginning without algo}
% \subsection{Workflow}
% \begin{algorithm}[thb]
%   \begin{algorithmic}
%     \footnotesize
%     \State \textbf{Input:} $D$ -- dataset, \constraints -- constraints, \dependencies -- dependencies \\(optional: tables $T$, groups $G$)
%     \State \textbf{Output:} $S$ -- learned constraints with their satisfaction assignment
%     \If{$T$ is \textbf{not} provided}
%       \State $T \gets \extracttables(D)$
%     \EndIf
%     \If{$G$ is \textbf{not} provided}
%       \State $G \gets \extractgroups(D, T)$
%     \EndIf
%     \State $S \gets \learnconstraints(G,\constraints,\dependencies)$
%     \State \Return $S$
% \end{algorithmic}
% \caption{Workflow}
% \label{algo:workflow}
% \end{algorithm}

% \textbf{Approach}
% \begin{itemize}
%   \item Notation
%   \item Algorithm (select constraints, find assignments, find solutions)
% \end{itemize}

% \samuel{Move next to subgroup satisfaction search}
% \section{Declarative modeling}
% \sergey{We need to fit ASP, Minizinc and all that here, I mean it is supposed to be an important point after all}
